---
title: "PPG Paint Colors: Final Project"
subtitle: "Part-1: Data Exploration"
author: "Navodita Mathur"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

This RMarkdown shows how to explore the final project data. 

## Load packages

```{r, load_tidyverse}
library(tidyverse)
```

## Read data

The code chunk below reads in the final project data.  
```{r, read_final_data}
df <- readr::read_csv("paint_project_train_data.csv", col_names = TRUE)
```

The `readr::read_csv()` function displays the data types and column names associated with the data. However, a glimpse is shown below that reveals the number of rows and also shows some of the representative values for the columns.  

```{r, show_data_glimpse}
df %>% glimpse()
```

The data consist of continuous and categorical inputs. The `glimpse()` shown above reveals the data type for each variable which state to you whether the input is continuous or categorical. The RGB color model inputs, `R`, `G`, and `B` are continuous (dbl) inputs. The HSL color model inputs consist of 2 categorical inputs, `Lightness` and `Saturation`, and a continuous input, `Hue`. Two outputs are provided. The continuous output, `response`, and the Binary output, `outcome`. However, the data type of the Binary outcome is numeric because the Binary `outcome` is **encoded** as `outcome = 1` for the EVENT and `outcome = 0` for the NON-EVENT.  

# Missing Values

```{r}
visdat::vis_miss(df) +
  theme(axis.text.x = element_text(size = 6.5, angle = 90))
```

```{r}
visdat::vis_dat(df)
```

The code chunk below shows summary of the data
```{r}
df%>%summary()
```

# Explore the data

## Visualize the distributions of variables in the data set

The code chunk below visualizes the distribution of data with respect to "R" using density plot
```{r}
df%>%
  ggplot(mapping=aes(x=R)) + 
  geom_density() + 
  geom_vline(aes(xintercept=mean(R)),
            color="blue", linetype="dashed", linewidth=1)+
  theme_bw()
```

The code chunk below visualizes the distribution of data with respect to "G" using density plot
```{r}
df%>%
  ggplot(mapping=aes(x=G)) + 
  geom_density() + 
  geom_vline(aes(xintercept=mean(G)),
            color="blue", linetype="dashed", linewidth=1)+
  theme_bw()
```

The code chunk below visualizes the distribution of data with respect to "B" using density plot
```{r}
df%>%
  ggplot(mapping=aes(x=B)) + 
  geom_density() + 
  geom_vline(aes(xintercept=mean(B)),
            color="blue", linetype="dashed", linewidth=1) +
  theme_bw()
```

The code chunk below visualizes the distribution of data with respect to "Hue" using density plot
```{r}
df%>%
  ggplot(mapping=aes(x=Hue)) + 
  geom_density() + 
  geom_vline(aes(xintercept=mean(Hue)),
            color="blue", linetype="dashed", linewidth=1)+
  theme_bw()
```

The code chunk below visualizes the distribution of data with respect to "Lightness" using a bar plot
```{r}
df%>%
  ggplot()+
  geom_bar(mapping=aes(x=Lightness))+
  theme_bw()
```

The code chunk below visualizes the distribution of data with respect to "Saturation"  using a bar plot
```{r}
df%>%
  ggplot()+
  geom_bar(mapping=aes(x=Saturation))+
  theme_bw()
```

## Condition (group) the continuous variables based on the categorical variables

The below code visualizes density plot of R by grouping Lightness
```{r}
df%>%
  ggplot(mapping=aes(x=R, color=Lightness)) + 
  geom_density() +
  theme_bw()
```

The below code visualizes density plot of R by grouping Saturation
```{r}
df%>%
  ggplot(mapping=aes(x=R, color=Saturation)) + 
  geom_density() +
  theme_bw()
```

The below code visualizes density plot of G by grouping  Lightness
```{r}
df%>%
  ggplot(mapping=aes(x=G, color=Lightness)) + 
  geom_density() +
  theme_bw()
```

The below code visualizes density plot of G by grouping  Saturation
```{r}
df%>%
  ggplot(mapping=aes(x=G, color=Saturation)) + 
  geom_density() +
  theme_bw()
```

The below code visualizes density plot of B by grouping Lightness
```{r}
df%>%
  ggplot(mapping=aes(x=B, color=Lightness)) + 
  geom_density() +
  theme_bw()
```

The below code visualizes density plot of B by grouping Saturation
```{r}
df%>%
  ggplot(mapping=aes(x=B, color=Saturation)) + 
  geom_density() +
  theme_bw()
```

The below code visualizes density plot of Hue by grouping Lightness
```{r}
df%>%
  ggplot(mapping=aes(x=Hue, color=Lightness)) + 
  geom_density() +
  theme_bw()
```

The below code visualizes density plot of Hue by grouping Saturation
```{r}
df%>%
  ggplot(mapping=aes(x=Hue, color=Saturation)) + 
  geom_density() +
  theme_bw()
```

## Visualize the statistics

The below code visualizes the statistics of the continuous variables using boxplots
```{r}
 df %>% 
  tibble::rowid_to_column() %>%
  pivot_longer(c(R, G, B,Hue)) %>%
  ggplot(mapping = aes(x=name, y=value))+
  geom_boxplot(mapping = aes(group=name))+
  theme_bw()
```

The below code visualizes the proportion of data with respect to categorical variables
```{r}
df %>% 
  mutate(Lightness = forcats::fct_lump_prop(Lightness, 0.05),
         Saturation = forcats::fct_lump_prop(Saturation, 0.05)) %>% 
  count(Lightness, Saturation) %>% 
  mutate(prop_total = n / sum(n)) %>% 
  ggplot(mapping = aes(x = Lightness, y = Saturation)) +
  geom_tile(mapping = aes(fill = cut(prop_total,
                                     breaks = seq(0.0, 0.03, by = 0.001))),
            color = "black") +
  geom_text(mapping = aes(label = signif(prop_total, 3),
                          color = prop_total < 0.13)) +
  scale_fill_viridis_d("Proportion") +
  scale_color_manual(guide = 'none',
                     values = c("TRUE" = "white", 
                                "FALSE" = "black")) +
  theme_bw()
```

The below code visualizes the proportion of data for different categories of Lightness

```{r}
df%>% 
  count(Lightness) %>% 
  knitr::kable()
```

```{r}
 df%>% 
  mutate(Lightness = forcats::fct_infreq(Lightness)) %>% 
  ggplot(mapping = aes(x = Lightness, y = after_stat(prop), group = 1)) +
  geom_bar() +
  coord_flip() +
  labs(x = "") +
  theme_bw()
```

The below code visualizes the proportion of data for different categories of  Saturation

```{r}
df%>% 
  count(Saturation) %>% 
  knitr::kable()
```

```{r}
 df%>% 
  mutate(Saturation = forcats::fct_infreq(Saturation)) %>% 
  ggplot(mapping = aes(x = Saturation, y = after_stat(prop), group = 1)) +
  geom_bar() +
  coord_flip() +
  labs(x = "") +
  theme_bw()
```

## Visualize the relationships between the continuous inputs, are they correlated

```{r}
pairs <- model.matrix(response~0+R+G+B+Hue, df)
pairs %>% cor %>% corrplot::corrplot(type = 'upper',method='square')
```

## Visualize the relationships between the continuous outputs (response and the LOGIT-transformed response, y) with respect to the INPUTS

### Visualize the relationships between the continuous output 'response' with respect to the inputs

-> Visualize the relationships between the continuous output 'response' with respect to the continuous inputs

```{r}
 df %>% 
  tibble::rowid_to_column() %>%
  pivot_longer(c(R, G, B,Hue)) %>%
  ggplot(mapping = aes(x=value,y=response))+
  geom_point(alpha=0.33)+
  facet_wrap(~name,scales = 'free_x')+
  theme_bw()
```

The below code visualizes the relationship between response and R
```{r}
df%>%
  ggplot(mapping=aes(y=response))+
  geom_point(mapping=aes(x=R))+
  theme_bw()
```

The below code visualizes the relationship between response and G
```{r}
df%>%
  ggplot(mapping=aes(y=response))+
  geom_point(mapping=aes(x=G))+
  theme_bw()
```
  
The below code visualizes the relationship between response and B
```{r}
df%>%
  ggplot(mapping=aes(y=response))+
  geom_point(mapping=aes(x=B))+
  theme_bw()
```

The below code visualizes the relationship between response and Hue
```{r}
df%>%
  ggplot(mapping=aes(y=response))+
  geom_point(mapping=aes(x=Hue))+
  theme_bw()
```

-> Visualize the relationships between the continuous output 'response' with respect to the categorical inputs

The below code visualizes the relationship between response and Lightness
```{r}
df%>%
  ggplot(mapping=aes(y=response))+
  geom_boxplot(mapping=aes(x=Lightness))+
  theme_bw()
```

The below code visualizes the relationship between response and Saturation
```{r}
df%>%
  ggplot(mapping=aes(y=response))+
  geom_boxplot(mapping=aes(x=Saturation))+
  theme_bw()
```

### Visualize the relationships between the continuous output the LOGIT-transformed response, y) with respect to the inputs

```{r}
df <- df %>% 
  mutate(y = boot::logit( (response - 0) / (100 - 0) ) )

df %>% glimpse()
```

-> Visualize the relationships between the continuous output the LOGIT-transformed response, y) with respect to the continuous inputs

```{r}
df %>% 
  tibble::rowid_to_column() %>%
  pivot_longer(c(R, G, B,Hue)) %>%
  ggplot(mapping = aes(x=value,y=y))+
  geom_point(alpha=0.33)+
  facet_wrap(~name,scales = 'free_x')+
  theme_bw()
```

The below code visualizes the relationships between the continuous output the LOGIT-transformed response, y)and  R
```{r}
df%>%
  ggplot(mapping=aes(y=y))+
  geom_point(mapping=aes(x=R))+
  theme_bw()
```

The below code visualizes the relationships between the continuous output the LOGIT-transformed response, y) and G
```{r}
df%>%
  ggplot(mapping=aes(y=y))+
  geom_point(mapping=aes(x=G))+
  theme_bw()
```

The below code visualizes the relationships between the continuous output the LOGIT-transformed response, y) and B
```{r}
df%>%
  ggplot(mapping=aes(y=y))+
  geom_point(mapping=aes(x=B))+
  theme_bw()
```

The below code visualizes the relationships between the continuous output the LOGIT-transformed response, y) and Hue
```{r}
df%>%
  ggplot(mapping=aes(y=y))+
  geom_point(mapping=aes(x=Hue))+
  theme_bw()
```

-> Visualize the relationships between the continuous output the LOGIT-transformed response, y) with respect to the categorical inputs

The below code visualizes the relationships between the continuous output the LOGIT-transformed response, y) and Lightness
```{r}
df%>%
  ggplot(mapping=aes(y=y))+
  geom_boxplot(mapping=aes(x=Lightness))+
  theme_bw()
```

The below code visualizes the relationships between the continuous output the LOGIT-transformed response, y) and Saturation
```{r}
df%>%
  ggplot(mapping=aes(y=y))+
  geom_boxplot(mapping=aes(x=Saturation))+
  theme_bw()
```

## Visualize the relationships between the continuous output the LOGIT-transformed response, y) with respect to the inputs and binary outcome

```{r}
 df %>% 
  tibble::rowid_to_column() %>%
  pivot_longer(c(R, G, B,Hue)) %>%
  ggplot(mapping = aes(x=value,y=y,color=outcome))+
  geom_point(alpha=0.33)+
  facet_wrap(~name, scales = 'free_x')+
  theme_bw()
```

## Visualize the behavior of the binary outcome 

### Visualize the behavior of the binary outcome with respect to the continuous inputs

The below code visualizes the behavior of the binary outcome with respect to R
```{r}
df%>%
  ggplot(mapping=aes(y=outcome))+
  geom_point(mapping=aes(x=R))+
  theme_bw()
```

The below code visualizes the behavior of the binary outcome with respect to G
```{r}
df%>%
  ggplot(mapping=aes(y=outcome))+
  geom_point(mapping=aes(x=G))+
  theme_bw()
```

The below code visualizes the behavior of the binary outcome with respect to B
```{r}
df%>%
  ggplot(mapping=aes(y=outcome))+
  geom_point(mapping=aes(x=B))+
  theme_bw()
```

The below code visualizes the behavior of the binary outcome with respect to Hue
```{r}
df%>%
  ggplot(mapping=aes(y=outcome))+
  geom_point(mapping=aes(x=Hue))+
  theme_bw()
```

### visualize the behavior of the binary outcome with respect to the categorical inputs

The below code visualizes the behavior of the binary outcome with respect to Lightness using boxplots
```{r}
df%>%
  ggplot(mapping=aes(y=outcome))+
  geom_boxplot(mapping=aes(x=Lightness))+
  theme_bw()
```

The below code visualizes the behavior of the binary outcome with respect to Saturation  using boxplots
```{r}
df%>%
  ggplot(mapping=aes(y=outcome))+
  geom_boxplot(mapping=aes(x=Saturation))+
  theme_bw()
```

The below code visualizes the behavior of the binary outcome with respect to Lightness using bar plots
```{r}
df%>%
  ggplot(mapping=aes(Lightness,fill=as.factor(outcome)))+
  geom_bar()+
  theme_bw()
```

The below code visualizes the behavior of the binary outcome with respect to Saturation using bar plots
```{r}
df%>%
  ggplot(mapping=aes(Saturation,fill=as.factor(outcome)))+
  geom_bar()+
  theme_bw()
```

The below code visualizes the behavior of the binary outcome with respect to Lightness using bar plots through proportion
```{r}
df%>%
  ggplot(mapping=aes(Lightness,fill=as.factor(outcome)))+
  geom_bar(position = "fill")+
  theme_bw()
```

The below code visualizes the behavior of the binary outcome with respect to Saturation using bar plots through proportion
```{r}
df%>%
  ggplot(mapping=aes(Saturation,fill=as.factor(outcome)))+
  geom_bar(position = "fill")+
  theme_bw()
```

## Additional Visualizations to analyse behavior of outcome for continuous inputs

```{r}
df %>% 
  tibble::rowid_to_column() %>%
  pivot_longer(c(R, G, B,Hue)) %>%
  ggplot(mapping=aes(x=value,y=outcome))+
  geom_jitter(height=0.02,width=0)+
  facet_wrap(~name,scales = 'free_x')+
  theme_bw()
```

```{r}
df %>% 
  tibble::rowid_to_column() %>%
  pivot_longer(c(R, G, B,Hue)) %>%
  ggplot(mapping=aes(x=value,y=outcome))+
  geom_jitter(height=0.02,width=0)+
  geom_smooth(formula=y~x, method = "glm" , method.args = list(family = 'binomial'))+
  facet_wrap(~name,scales = 'free_x')+
  theme_bw()
```

## Visualize the behavior of continuous inputs with respect to categorical inputs

The below code visualizes the behavior of continuous inputs with respect to Lightness through points

```{r}
 df %>% 
  tibble::rowid_to_column() %>%
  pivot_longer(c(R, G, B,Hue)) %>%
  ggplot(mapping = aes(x=Lightness,y=value))+
  geom_point(alpha=0.33)+
  facet_wrap(~name, scales = 'free_y')+
  theme_bw()
```

The below code visualizes the behavior of continuous inputs with respect to Lightness through boxplots
```{r}
 df %>% 
  tibble::rowid_to_column() %>%
  pivot_longer(c(R, G, B,Hue)) %>%
  ggplot(mapping = aes(x=Lightness,y=value))+
  geom_boxplot()+
  facet_wrap(~name, scales = 'free_y')+
  theme_bw()
```

The below code visualizes the behavior of continuous inputs with respect to Saturation through points
```{r}
 df %>% 
  tibble::rowid_to_column() %>%
  pivot_longer(c(R, G, B,Hue)) %>%
  ggplot(mapping = aes(x=Saturation,y=value))+
  geom_point(alpha=0.33)+
  facet_wrap(~name, scales = 'free_y')+
  theme_bw()
```

The below code visualizes the behavior of continuous inputs with respect to Saturation through boxplots
```{r}
 df %>% 
  tibble::rowid_to_column() %>%
  pivot_longer(c(R, G, B,Hue)) %>%
  ggplot(mapping = aes(x=Saturation,y=value))+
  geom_boxplot()+
  facet_wrap(~name, scales = 'free_y')+
  theme_bw()
```

# Check for linear separability between variables

If the points can be completely separated vertically using a line then the data is said to be linearly separable. Models can be difficult to fit for such data.

The below code visualizes the linear separability between R and G
```{r}
df%>%  
  ggplot(mapping = aes(x = R, y = G))+
  geom_point(mapping=aes(color=as.factor(outcome),shape=as.factor(outcome)),size=3)+
  theme_bw()
```

The below code visualizes the linear separability between R and B
```{r}
df%>%  
  ggplot(mapping = aes(x = R, y = B))+
  geom_point(mapping=aes(color=as.factor(outcome),shape=as.factor(outcome)),size=3)+
  theme_bw()
```

The below code visualizes the linear separability between R and Hue
```{r}
df%>%  
  ggplot(mapping = aes(x = R, y = Hue))+
  geom_point(mapping=aes(color=as.factor(outcome),shape=as.factor(outcome)),size=3)+
  theme_bw()
```

The below code visualizes the linear separability between G and B
```{r}
df%>%  
  ggplot(mapping = aes(x = G, y = B))+
  geom_point(mapping=aes(color=as.factor(outcome),shape=as.factor(outcome)),size=3)+
  theme_bw()
```

The below code visualizes the linear separability between G and Hue
```{r}
df%>%  
  ggplot(mapping = aes(x = G, y = Hue))+
  geom_point(mapping=aes(color=as.factor(outcome),shape=as.factor(outcome)),size=3)+
  theme_bw()
```

The below code visualizes the linear separability between B and Hue
```{r}
df%>%  
  ggplot(mapping = aes(x = B, y = Hue))+
  geom_point(mapping=aes(color=as.factor(outcome),shape=as.factor(outcome)),size=3)+
  theme_bw()
```

Let us visualize the same for different categorical variables

The below code visualizes the linear separability between R and G with respect to Lightness
```{r}
df%>%  
  ggplot(mapping = aes(x = R, y = G))+
  geom_point(mapping=aes(color=as.factor(outcome),shape=as.factor(outcome)),size=3)+
  facet_wrap(~Lightness, scales = "free")+
  theme_bw()
```

The below code visualizes the linear separability between R and B with respect to Lightness
```{r}
df%>%  
  ggplot(mapping = aes(x = R, y = B))+
  geom_point(mapping=aes(color=as.factor(outcome),shape=as.factor(outcome)),size=3)+
  facet_wrap(~Lightness, scales = "free")+
  theme_bw()
```

The below code visualizes the linear separability between R and Hue with respect to Lightness
```{r}
df%>%  
  ggplot(mapping = aes(x = R, y = Hue))+
  geom_point(mapping=aes(color=as.factor(outcome),shape=as.factor(outcome)),size=3)+
  facet_wrap(~Lightness, scales = "free")+
  theme_bw()
```

The below code visualizes the linear separability between G and B with respect to Lightness
```{r}
df%>%  
  ggplot(mapping = aes(x = G, y = B))+
  geom_point(mapping=aes(color=as.factor(outcome),shape=as.factor(outcome)),size=3)+
  facet_wrap(~Lightness, scales = "free")+
  theme_bw()
```

The below code visualizes the linear separability between G and Hue with respect to Lightness
```{r}
df%>%  
  ggplot(mapping = aes(x = G, y = Hue))+
  geom_point(mapping=aes(color=as.factor(outcome),shape=as.factor(outcome)),size=3)+
  facet_wrap(~Lightness, scales = "free")+
  theme_bw()
```

The below code visualizes the linear separability between B and Hue with respect to Lightness
```{r}
df%>%  
  ggplot(mapping = aes(x = B, y = Hue))+
  geom_point(mapping=aes(color=as.factor(outcome),shape=as.factor(outcome)),size=3)+
  facet_wrap(~Lightness, scales = "free")+
  theme_bw()
```

The below code visualizes the linear separability between R and G with respect to Saturation
```{r}
df%>%  
  ggplot(mapping = aes(x = R, y = G))+
  geom_point(mapping=aes(color=as.factor(outcome),shape=as.factor(outcome)),size=3)+
  facet_wrap(~Saturation, scales = "free")+
  theme_bw()
```

The below code visualizes the linear separability between R and B with respect to Saturation
```{r}
df%>%  
  ggplot(mapping = aes(x = R, y = B))+
  geom_point(mapping=aes(color=as.factor(outcome),shape=as.factor(outcome)),size=3)+
  facet_wrap(~Saturation, scales = "free")+
  theme_bw()
```

The below code visualizes the linear separability between R and Hue with respect to Saturation
```{r}
df%>%  
  ggplot(mapping = aes(x = R, y = Hue))+
  geom_point(mapping=aes(color=as.factor(outcome),shape=as.factor(outcome)),size=3)+
  facet_wrap(~Saturation, scales = "free")+
  theme_bw()
```

The below code visualizes the linear separability between G and B with respect to Saturation
```{r}
df%>%  
  ggplot(mapping = aes(x = G, y = B))+
  geom_point(mapping=aes(color=as.factor(outcome),shape=as.factor(outcome)),size=3)+
  facet_wrap(~Saturation, scales = "free")+
  theme_bw()
```

The below code visualizes the linear separability between G and Hue with respect to Saturation
```{r}
df%>%  
  ggplot(mapping = aes(x = G, y = Hue))+
  geom_point(mapping=aes(color=as.factor(outcome),shape=as.factor(outcome)),size=3)+
  facet_wrap(~Saturation, scales = "free")+
  theme_bw()
```

The below code visualizes the linear separability between B and Hue with respect to Saturation
```{r}
df%>%  
  ggplot(mapping = aes(x = B, y = Hue))+
  geom_point(mapping=aes(color=as.factor(outcome),shape=as.factor(outcome)),size=3)+
  facet_wrap(~Saturation, scales = "free")+
  theme_bw()
```
